mixModelE1data

### 2018-08-16 E2/analysis/mixModelE2data.Rmd
after partially migrated from GoogleDrive

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,  comment = NA)
# http://htmlpreview.github.io/?https://github.com/alexholcombe/MixtureModelRSVP/blob/master/compareMATLABtoR.html
```

@@

#Import raw data
dataPath<- file.path("Data/")
#Experiment was administered by MATLAB
#.mat file been preprocessed into melted long dataframe by importE1data.Rmd
data<- readRDS( file.path(dataPath, "backwards2E1_rawDataFromMAT.rda") )

@@

@@

Investigate whether the pathological identicalness of inverted/canonical is already at this point
```{r}
dg<- df %>% filter(subject < "AC")

@@

@@

estimates<- df  %>%  #  filter(subject=="AA") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

write.csv(estimates, file = "Results/backwards2E1_paramEstimates.csv")
#saveRDS(estimates, file = "Data/backwards2E1_paramEstimates.rda", compress="bzip2")

>>>>

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,  comment = NA)
```

@@

#Import data that was changed from MATLAB raw to R dataframe by importE2data.Rmd
dataPath<- file.path("..","Data")
#Experiment was administered by MATLAB
#.mat file been preprocessed into melted long dataframe by importE1data.Rmd
data<- readRDS( file.path(dataPath, "backwards2E2_rawDataFromMAT.rda") )

@@

Why are there NaNs for targetSP?
```{r}
table(is.nan(df$targetSP))

@@

Investigate whether pathological identicalness of inverted/canonical happens, that happened in E1 . Seems it doesn't

```{r}
dg<- df %>% filter(subject < "AC")

@@

Try to analyze one bit of data.
WHY ARE THERE NANS IN TARGETSP?
```{r}
library(mixRSVP)
dg<-df %>% filter(subject=="AA")
analyzeOneCondition(dg,numItemsInStream,parameterBounds(),nReplicates=5)

analyzeOneConditionDF(df %>% filter(subject=="AA"),numItemsInStream,parameterBounds(),nReplicates=5)

@@

estimates<- df  %>% filter(subject=="AA") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

write.csv(estimates, file = "Results/backwards2E2_paramEstimates.csv")
#saveRDS(estimates, file = "Data/backwards2E1_paramEstimates.rda", compress="bzip2")
